Key Provisioning for the Internet of Things via Light

### 2015-11-04 paper/Zusammenfassung.tex
add authors again, small fixes

% \numberofauthors{5}

% \author{
% \alignauthor
% Cornelius Bock
% %
% \alignauthor
% Daniel Werner
% %
% \alignauthor
% Felix Wolff
% %
% \and
% \texttt{\{cornelius.bock|daniel.werner|felix.wolff\}@student.hpi.de} \\ \\
% \and
% \alignauthor
% Prof. Dr. Christoph Meinel\\
%     \affaddr{\textit{Supervisor}}
% %
% \alignauthor
% Konrad-Felix Krentz\\
%     \affaddr{\textit{Supervisor}}
% }
\toappear{}
\maketitle

@@

We implemented a prototype for an Android smartphone and a mote running the Contiki OS.
Contiki is an open source, state-of-the-art operating system for IoT devices.
We also tested techniques to make the transmission reliable by using error detecting and correcting codes and examined their usefulness with regard to data overhead and transmisison speed.
Besides, we investigated the fastest transmission speed while maintaining a high chance of correctness.
Depending on the smartphone, transmission rates between 32 and 64 bits/s are within reach.
With regard to 128 bit keys, those rates are totally fine for a first prototype.
However performance varies a lot between different phone models.
We did not find a general reason for the performance differences yet.
More time needs to be invested in this topic.
Furthermore, future work should target the scaling of the presented method to initialize several motes at once.
This is a realistic scenario regarding IoT networks, where motes encrypt their communication using predistributed secret keys.
Also, one should conduct a user study to prove the usability of the prototype for users without strong technical background.

>>>>

\numberofauthors{5}

\author{
\alignauthor
Cornelius Bock
%
\alignauthor
Daniel Werner
%
\alignauthor
Felix Wolff
%
\and
\texttt{\{cornelius.bock|daniel.werner|felix.wolff\}@student.hpi.de} \\ \\
\and
\alignauthor
Prof. Dr. Christoph Meinel\\
    \affaddr{\textit{Supervisor}}
%
\alignauthor
Konrad-Felix Krentz\\
    \affaddr{\textit{Supervisor}}
}
\toappear{}
\maketitle

@@

We implemented a prototype for an Android smartphone and a mote running the Contiki OS.
Contiki is an open source, state-of-the-art operating system for IoT devices.
We also tested techniques to make the transmission reliable by using error detection and correcting codes and examined their usefulness with regard to data overhead and transmisison speed.
Besides, we investigated the fastest transmission speed while maintaining a high chance of correctness.
Depending on the smartphone, transmission rates between 32 and 64 bits/s are within reach.
With regard to 128 bit keys, those rates are definitely acceptable for a first prototype.
However performance varies a lot between different phone models.
We did not find a general reason for the performance differences yet.
More time needs to be invested in this topic.
Furthermore, future work should target the scaling of the presented method to initialize several motes at once.
This is a realistic scenario regarding IoT networks, where motes encrypt their communication using predistributed secret keys.
Also, one should conduct a user study to prove the usability of the prototype for users without strong technical background.
